HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-04-20 LaTeX/ms.tex
Wang final comments.

%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudders hayward cowley almalens
\author{R.~S.~Bussmann\altaffilmark{1},
D.~Riechers\altaffilmark{1},
A.~Fialkov\altaffilmark{2},
J.~Scudders\altaffilmark{3},
C.~C.~Hayward\altaffilmark{4,5},
W.~I.~Cowley\altaffilmark{6},
J.~Bock\altaffilmark{7,8},
J.~Calanog\altaffilmark{9},
S.~C.~Chapman\altaffilmark{10},
A.~Cooray\altaffilmark{9},
F.~De Bernardis\altaffilmark{9},
D.~Farrah\altaffilmark{11},
Hai~Fu\altaffilmark{12},
R.~Gavazzi\altaffilmark{13},
R.~Hopwood\altaffilmark{14},
R.~J.~Ivison\altaffilmark{15,16},
M.~Jarvis\altaffilmark{17},
C.~Lacey\altaffilmark{6},
A.~Loeb\altaffilmark{5},
S.~J.~Oliver\altaffilmark{3},
I.~P{\'e}rez-Fournon\altaffilmark{18,19},
D.~Rigopoulou\altaffilmark{20,21},
I.~G.~Roseboom\altaffilmark{3,16},
Douglas~Scott\altaffilmark{22},
A.~J.~Smith\altaffilmark{3},
J.~D.~Vieira\altaffilmark{23},
L.~Wang\altaffilmark{6},
J.~Wardlow\altaffilmark{24}}
\altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
instruments provided by European-led Principal Investigator consortia and with
important participation from NASA.}
\altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
\altaffiltext{2}{Departement de Physique, Ecole Normale Superieure, CNRS, 24 rue Lhomond, 75005 Paris, France}
\altaffiltext{3}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
\altaffiltext{4}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
\altaffiltext{7}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
\altaffiltext{8}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
\altaffiltext{9}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
\altaffiltext{10}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
\altaffiltext{11}{Department of Physics, Virginia Tech, Blacksburg, VA 24061}
\altaffiltext{12}{Department of Physics and Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}
\altaffiltext{13}{Institut d'Astrophysique de Paris, UMR 7095, CNRS, UPMC Univ. Paris 06, 98bis boulevard Arago, F-75014 Paris, France}
\altaffiltext{14}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
\altaffiltext{15}{UK Astronomy Technology Centre, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{16}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{17}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{18}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{19}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{20}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
\altaffiltext{21}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
\altaffiltext{22}{Department of Physics \& Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T~1Z1, Canada}
\altaffiltext{23}{Department of Astronomy and Department of Physics, University of Illinois, 1002 West Green Street, Urbana, IL 61801}
\altaffiltext{24}{Dark Cosmology Centre, Niels Bohr Institute, University of
Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}

@@

The sample was selected to be the 29 brightest DSFGs in the Southern sky that
are not known radio AGN, nearby late-type galaxies, or Galactic emission. The
selection was designed to assemble a large sample of lensed galaxies in the
ALMA-accesible HerMES fields, and was constructed from the SUSSEXtractor
catalogs, which were available prior to the ALMA Cycle~0 deadline.
Subsequently, improved efforts to deblend SPIRE photometry at 500$\,\mu$m using
StarFinder \citep{Wang:2014lr} were introduced that formed the basis of the
lens selection criteria used in \citet{Wardlow:2013lr}.  As a result of the
improved deblending algorithms in the StarFinder catalogues and
\citet{Wardlow:2013lr} a number of objects in our sample have significantly
lower $S_{500}$ values in the StarFinder catalog than in the original
SUSSEXtractor catalogs.  This and further investigation into the StarFinder
catalogs shows that their original flux was boosted by blending with nearby
sources rather than by gravitational lensing.  For this reason, the objects in
this sample comprise a combination of lenses and blends of multiple sources.

>>>>

%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudders hayward cowley almalens
\author{R.~S.~Bussmann\altaffilmark{1},
D.~Riechers\altaffilmark{1},
A.~Fialkov\altaffilmark{2},
J.~Scudders\altaffilmark{3},
C.~C.~Hayward\altaffilmark{4,5},
W.~I.~Cowley\altaffilmark{6},
J.~Bock\altaffilmark{7,8},
J.~Calanog\altaffilmark{9},
S.~C.~Chapman\altaffilmark{10},
A.~Cooray\altaffilmark{9},
F.~De Bernardis\altaffilmark{9},
D.~Farrah\altaffilmark{11},
Hai~Fu\altaffilmark{12},
R.~Gavazzi\altaffilmark{13},
R.~Hopwood\altaffilmark{14},
R.~J.~Ivison\altaffilmark{15,16},
M.~Jarvis\altaffilmark{17},
C.~Lacey\altaffilmark{6},
A.~Loeb\altaffilmark{5},
S.~J.~Oliver\altaffilmark{3},
I.~P{\'e}rez-Fournon\altaffilmark{18,19},
D.~Rigopoulou\altaffilmark{20,21},
I.~G.~Roseboom\altaffilmark{3,16},
Douglas~Scott\altaffilmark{22},
A.~J.~Smith\altaffilmark{3},
J.~D.~Vieira\altaffilmark{23},
L.~Wang\altaffilmark{6,24},
J.~Wardlow\altaffilmark{25}}
\altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
instruments provided by European-led Principal Investigator consortia and with
important participation from NASA.}
\altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
\altaffiltext{2}{Departement de Physique, Ecole Normale Superieure, CNRS, 24 rue Lhomond, 75005 Paris, France}
\altaffiltext{3}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
\altaffiltext{4}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
\altaffiltext{7}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
\altaffiltext{8}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
\altaffiltext{9}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
\altaffiltext{10}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
\altaffiltext{11}{Department of Physics, Virginia Tech, Blacksburg, VA 24061}
\altaffiltext{12}{Department of Physics and Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}
\altaffiltext{13}{Institut d'Astrophysique de Paris, UMR 7095, CNRS, UPMC Univ. Paris 06, 98bis boulevard Arago, F-75014 Paris, France}
\altaffiltext{14}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
\altaffiltext{15}{UK Astronomy Technology Centre, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{16}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{17}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{18}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{19}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{20}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
\altaffiltext{21}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
\altaffiltext{22}{Department of Physics \& Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T~1Z1, Canada}
\altaffiltext{23}{Department of Astronomy and Department of Physics, University of Illinois, 1002 West Green Street, Urbana, IL 61801}
\altaffiltext{24}{SRON Netherlands Institute for Space Research, Landleven 12, 9747 AD, Groningen, The Netherlands}
\altaffiltext{25}{Dark Cosmology Centre, Niels Bohr Institute, University of
Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}

@@

The sample was selected to be the 29 brightest DSFGs in the Southern sky that
are not known radio AGN, nearby late-type galaxies, or Galactic emission. The
selection was designed to assemble a large sample of lensed galaxies in the
ALMA-accesible HerMES fields, and was constructed from the SUSSEXtractor
catalogs \citep{Smith:2012uq}, which were available prior to the ALMA Cycle~0
deadline.  Subsequently, improved efforts to deblend SPIRE photometry at
500$\,\mu$m using StarFinder \citep{Wang:2014lr} were introduced that formed
the basis of the lens selection criteria used in \citet{Wardlow:2013lr}.  As a
result of the improved deblending algorithms in the StarFinder catalogues and
\citet{Wardlow:2013lr} a number of objects in our sample have significantly
lower $S_{500}$ values in the StarFinder catalog than in the original
SUSSEXtractor catalogs.  This and further investigation into the StarFinder
catalogs shows that their original flux was boosted by blending with nearby
sources rather than by gravitational lensing.  For this reason, the objects in
this sample comprise a combination of lenses and blends of multiple sources.
